How to compute the fusion product of MV cycles in type A

### 2021-05-15 draft.tex

% \begin{example}
    \[
        \tau = \young(1112,23) \qquad \gt(\tau) = \begin{matrix}
            3 \\
            4 & 1 \\ 
            4 & 2 & 0 
        \end{matrix} \qquad n_\bullet(\tau) = (1,0,1) %\,. 
    \]
% \end{example}
% For example, if 
% \[
%     \tau = \young(1112,23) 
% \]
% then
% \begin{gather*}
% %    \text{if } \tau = \young(1112,23) \text{ then } 
% \gt(\tau) = \begin{matrix}
%        3 \\
%        4 & 1 \\ 
%        4 & 2 & 0 
%    \end{matrix} \text{ and }
%    n_\bullet(\tau) = (1,0,1)\,. 
% \end{gather*}
% 
%This combinatorics is relevant because by work of the third author the MV cycles are parametrized by Lusztig data. (This holds much more generally than the present scope.)
% 
We can associate to $\tau$ the MV cycle $Z(\tau)=\overline{\mathring Z(\tau)}$ where
%  
\begin{equation*}
    \mathring Z(\tau) = 
    %  \overline{
        \{
            L\in S^\mu : L\cap\cO^i\in\Gr^{\lambda(i)}\text{ for } i = 1, \dots m 
        \} \,. 
    %  }
\end{equation*}
%

@@

Recall that $ S^\mu = N_-(\cK) t^\mu$.  For the purposes of this proof, we also introduce the notation $S^\mu_+ := N(\cK)t^\mu$. \acom{Sort out notation, do we no longer need $S_-, N_-$?}

First, we consider
\begin{equation*}
Z(\tau)_1 := \{ L \in S^\mu : L \cap \cO^i \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\}  
%Z(\tau)_2 := \{ L \in S^\mu : L \cap \cO^i \in S^{\lambda(i)} \cap \Gr^{\lambda(i)} \text{ for } i = 1, \dots m\}
\end{equation*}
From \cite[Corollary 9.7]{kamnitzer2010mirkovic}, we see that $ Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))^T$, where $ A(n_\bullet)$ is defined in section 4.3 of \cite{kamnitzer2010mirkovic}.  Thus, $ \overline{Z(\tau_1)}$ is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $.  We also note that $Z(\tau_1) \cap \Gr^\lambda$ is dense in $ Z(\tau_1)$.  
\jcom{Need to justify this last sentence.}

Fix $ i \in \{1, \dots, m\}$. If $ L \in S^\mu$, then $ L \cap \cO^i \in S^{\mu(i)}$.  Thus, we get a map $$ f_i : Z(\tau)_1 \rightarrow S^{\mu(i)} \cap S_+^{\lambda(i)} $$
From the definition of $ Z(\tau)_1 $, we see that $ f_i(Z(\tau_1) = Z(\tau(i)_1)$.  From above $ \Gr^{\lambda(i)} \cap f_i(Z(\tau(i)_1))$ is a dense constructible subset of $Z(\tau(i)_1)$.  Since $ Z(\tau)_1$ is irreducible, this implies that $ f_i^{-1}(S^{\mu(i)} \cap S_+^{\lambda(i)} \cap \Gr^{\lambda(i)}) $ is a dense constructible subset of $ Z(\tau_1) $.

>>>>

% \begin{example}
    \[
        \tau = \young(1112,23) \qquad \gt(\tau) = \begin{matrix}
            3 \\
            4 & 1 \\ 
            4 & 2 & 0 
        \end{matrix} \qquad n_\bullet(\tau) = (1,0,1) %\,. 
    \]
% \end{example}
% For example, if 
% \[
%     \tau = \young(1112,23) 
% \]
% then
% \begin{gather*}
% %    \text{if } \tau = \young(1112,23) \text{ then } 
% \gt(\tau) = \begin{matrix}
%        3 \\
%        4 & 1 \\ 
%        4 & 2 & 0 
%    \end{matrix} \text{ and }
%    n_\bullet(\tau) = (1,0,1)\,. 
% \end{gather*}
% 
%This combinatorics is relevant because by work of the third author the MV cycles are parametrized by Lusztig data. (This holds much more generally than the present scope.)
%

We will need the following definitions.
\begin{definition}
Let $ L \subset \OO^m$ be a point in $ \Grth$.  We define the relative dimension of $L $ by
$$
\rdim(L) := \dim_\CC \OO^m/L
$$

If $ \gamma \subset \{1, \dots, m\}$, then we define
\begin{gather*}
    \OO^\gamma := \Sp_{\OO}(e_i : i \in \gamma) \\
L^\gamma:= L \cap \OO^\gamma \subset \OO^\gamma \quad L_\gamma := L / L^{\gamma^c} \subset \OO^\gamma
\end{gather*}
where $ \gamma^c := \{1, \dots, m \} \setminus \gamma$.
\end{definition}

\begin{lemma}
    For any $ L \in \Grth$ and any $ 
    \gamma \subset \{1, \dots, m\} $, we have $ \rdim L_\gamma + \rdim L^{\gamma^c} = \rdim L$.
\end{lemma}
We let $ D_\gamma(L) := \rdim L_\gamma$. By \cite[Proposition 9.3]{kamnitzer2010mirkovic}, this coincides with the general definition of $ D_\gamma$ given in that paper.

\jcom{There is a discrepancy regarding $ \gamma$ and $ \gamma^c$.}

Recall that $ S^\mu = N_-(\cK) t^\mu$. We also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.

\begin{lemma} \label{le:Srdim}
    Let $ L \in \Grth$.  The following are equivalent:
    \begin{enumerate}
        \item $ L \in S_+^\mu$
        \item $ \rdim L^{\{1, \dots, i\}} = \mu_1 + \dots + \mu_i$ for all $ i = 1, \dots, m $.
        \item $ \rdim L_{\{i+1, \dots, m\}} = \mu_{i+1} + \dots + \mu_m$ for $ i  = 1, \dots, m$.
    \end{enumerate}
    The same statement hold for $ S_-^\mu$ with the $ L^\gamma$ changed to $ L_\gamma$ above.
\end{lemma}

We can associate to $\tau$ an MV cycle.   
%  
\begin{equation*}
    \mathring Z(\tau) = 
    %  \overline{
        \{
            L\in S^\mu : L_{\{1, \dots, i\}} \in\Gr^{\lambda(i)}\text{ for } i = 1, \dots m 
        \}\,. 
     }
\end{equation*}
% 
\jcom{Maybe use $ [m] $ for $\{1, \dots, m\}$ ?}

@@

First, we consider
\begin{equation*}
Z(\tau)_1 := \{ L \in S^\mu : L_{\{1, \dots, i\}} \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\}  
%Z(\tau)_2 := \{ L \in S^\mu : L \cap \cO^i \in S^{\lambda(i)} \cap \Gr^{\lambda(i)} \text{ for } i = 1, \dots m\}
\end{equation*}

Using Lemma \ref{le:Srdim}, we see that
$$
Z(\tau)_1 = \{ L \in S^\mu : \rdim L_{\{j, \dots, i\}} = \lambda(i)_j + \dots + \lambda(i)_i
$$

From  the proof of \cite[Proposition 9.6]{kamnitzer2010mirkovic}, we see that $ Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))$, where $ A(n_\bullet)$ is defined in section 4.3 of \cite{kamnitzer2010mirkovic}.  Thus, $ \overline{Z(\tau_1)}$ is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $.  We also note that $Z(\tau_1) \cap \Gr^\lambda$ is dense in $ Z(\tau_1)$.  
\jcom{Need to justify this last sentence.}

Fix $ i \in \{1, \dots, m\}$. If $ L \in S^\mu$, then $ L_{\{1, \dots, i\}} \in S^{\mu(i)}$.  Thus, we get a map $$ f_i : Z(\tau)_1 \rightarrow S^{\mu(i)} \cap S_+^{\lambda(i)} $$
From the definition of $ Z(\tau)_1 $, we see that $ f_i(Z(\tau_1) = Z(\tau(i)_1)$.  From above $ \Gr^{\lambda(i)} \cap f_i(Z(\tau(i)_1))$ is a dense constructible subset of $Z(\tau(i)_1)$.  Since $ Z(\tau)_1$ is irreducible, this implies that $ f_i^{-1}(S^{\mu(i)} \cap S_+^{\lambda(i)} \cap \Gr^{\lambda(i)}) $ is a dense constructible subset of $ Z(\tau_1) $.
